### 2018-04-01 FrascatiPlot/Paper/NucleiB2.tex
adding generalised expression for CA

>>>>

- describe qualitatively what is visible in the figure that heavy-ion collisions are similar while production of "large" objects is suppressed in small collsion systmes

Following the approach and discussion presented in~\cite{KfirBlumPaper}, Eq.~\ref{eq:Cd} may be generalised as

\begin{equation}
\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
\label{eq:CA_general}
\end{equation}
%
for mass number $A$ and the radii $R_{i}$ which describe the volume of the emitting source.
